Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-13 VMCAI-revised-version/final.tex
section

@@

Let us recall that a system $\mathscr{S}=(S,\rightarrow, \leq)$ is \emph{downward compatible} \cite{DBLP:journals/tcs/FinkelS01} if
for all $s_1, s_2, t_1 \in S$ with
$s_2 \leq s_1$ and $s_1 \to t_1$
there
exists $t_2 \in S$ with
$t_2 \leq t_1$ and $s_2 \to^* t_2$.

@@

Let $D$ be a downward-closed subset of $S$
and let $x \in \downarrow \pred^*(D)$.
By downward closure, there exists
$y \in \pred^*(D)$ 
such that $x \leq y$.
By definition of $\pred^*(D)$ then there exists 
$d \in D$, $m\geq 0$ and $(a_i)_{0 \leq i \leq m+1} \in S^{m+2}$ such that
$y = a_0 \to a_1 \to a_2 \to \cdots \to a_m \to a_{m+1} = d$.

By downward compatibility $a_0 \to a_1$
implies that there exists $a'_1 \in S$ such that $a'_1 \leq a_1$ and
$x \to^* a'_1$.
More generally $a_i \to a_{i+1}$ and
$a'_i\leq a_i$ implies the existence of $a'_{i+1} \in S$ with $a'_{i+1} \leq a_{i+1}$ and
$a'_i \to^* a'_{i+1}$,
and, by induction,
 $x \to^* a'_1 \to^* \cdots \to^* a'_{m} \to^* a'_{m+1} = d'$
with $d' \leq d$.
Since
$d'$ 
belongs to $D$ by downward closure of $D$, $x \in \pred^*(D)$. \qed
\end{proof}

>>>>

There exists another type of WSTS which enjoy the downward compatibility.

\begin{definition}\cite{DBLP:journals/iandc/Finkel90,DBLP:journals/tcs/FinkelS01}
A {\em downward compatible well-structured transition system} (dc-WSTS)  $\mathscr{S}=(S, \rightarrow, \leq)$
is a transition system $(S, \rightarrow)$
equipped with a wqo ${\leq} \subseteq S \times S$ such that   
the transition relation $ \rightarrow$ is downward compatible with $\leq$, i.e., for all 
$s_1, t_1 , s_2 \in S$
	with $s_2 \leq s_1$  and $s_1 \rightarrow t_1$, there exists 
	$t_2 \in S$ with 
	$t_2 \leq t_1$ and $s_2 \rightarrow^{*} t_2$.
\end{definition}

Let us reformulate the downward compatibility property.

\begin{lemma}
For an ordered transition system $\mathscr{S}=(S, \rightarrow, \leq)$ (not necessarly a WSTS), the two following properties are equivalent: (1) $\mathscr{S}=(S, \rightarrow, \leq)$ is downward compatible; (2) for all downward-closed set $D \subseteq S$, the set $\pred_{\mathscr{S}}^*(D)$ is downward-closed.
\end{lemma}

To simplify the notations, we write without ambiguity  $\pred_{\mathscr{S}}^*(D)$ by  $\pred^*(D)$.
\begin{proof}
Let us prove $1 \implies 2$. 
Let $D$ be a downward-closed subset of $S$
and let $x \in \downarrow \pred^*(D)$.
By downward closure, there exists
$y \in \pred^*(D)$ 
such that $x \leq y$.
By definition of $\pred^*(D)$ then there exists 
$d \in D$, $m\geq 0$ and $(a_i)_{0 \leq i \leq m+1} \in S^{m+2}$ such that
$y = a_0 \to a_1 \to a_2 \to \cdots \to a_m \to a_{m+1} = d$.
%
By downward compatibility $a_0 \to a_1$
implies that there exists $a'_1 \in S$ such that $a'_1 \leq a_1$ and
$x \to^* a'_1$.
More generally $a_i \to a_{i+1}$ and
$a'_i\leq a_i$ implies the existence of $a'_{i+1} \in S$ with $a'_{i+1} \leq a_{i+1}$ and
$a'_i \to^* a'_{i+1}$,
and, by induction,
 $x \to^* a'_1 \to^* \cdots \to^* a'_{m} \to^* a'_{m+1} = d'$
with $d' \leq d$.
Since
$d'$ 
belongs to $D$ by downward closure of $D$, $x \in \pred^*(D)$ and then $\downarrow\pred^*(D) \subseteq \pred^*(D)$. Since $\pred^*(D) \subseteq \downarrow \pred^*(D)$ always hold, we deduce that $\pred^*(D)=\downarrow\pred^*(D)$ is downward-closed.

Let us prove $2 \implies 1$. Let $s_1, t_1 , s_2 \in S$ with $s_2 \leq s_1$  and $s_1 \rightarrow t_1$, Consider $\pred^*(\downarrow t_1)$; since $s_1 \rightarrow t_1$ we deduce that $s_1 \in \pred^*(\downarrow t_1)$, and since $s_2 \leq s_1$ and $\pred^*(\downarrow t_1)$ is downward-closed, we also have $s_2 \in \pred^*(\downarrow t_1)$. This means that there exists $t_2 \leq t_1$ such that 
$s_2 \rightarrow^{*} t_2$. Hence, we proved that $\mathscr{S}$ is downward compatible.
\qed

\end{proof}

@@

@@

%
%Let $D$ be a downward-closed subset of $S$
%and let $x \in \downarrow \pred^*(D)$.
%By downward closure, there exists
%$y \in \pred^*(D)$ 
%such that $x \leq y$.
%By definition of $\pred^*(D)$ then there exists 
%$d \in D$, $m\geq 0$ and $(a_i)_{0 \leq i \leq m+1} \in S^{m+2}$ such that
%$y = a_0 \to a_1 \to a_2 \to \cdots \to a_m \to a_{m+1} = d$.
%
%By downward compatibility $a_0 \to a_1$
%implies that there exists $a'_1 \in S$ such that $a'_1 \leq a_1$ and
%$x \to^* a'_1$.
%More generally $a_i \to a_{i+1}$ and
%$a'_i\leq a_i$ implies the existence of $a'_{i+1} \in S$ with $a'_{i+1} \leq a_{i+1}$ and
%$a'_i \to^* a'_{i+1}$,
%and, by induction,
% $x \to^* a'_1 \to^* \cdots \to^* a'_{m} \to^* a'_{m+1} = d'$
%with $d' \leq d$.
%Since
%$d'$ 
%belongs to $D$ by downward closure of $D$, $x \in \pred^*(D)$. \qed
\end{proof}
